The \dealii{} Library, Version 8.5

### 2017-03-20 8.5/paper.tex
clarify CellDataStorage

The \texttt{CellDataStorage} class is an integrated mechanism to
store user-defined data within each cell, such as a coefficient at each quadrature point.
Although the same was previously achieved through the use
of a cell \texttt{user\_pointer}, it required users to manage this data
themselves, including transfer of this data if ownership of a cell is
transferred from one processor to another in parallel
computations. Instead, this data is now treated as a first-class
citizen in \dealii{}.

\texttt{CellDataStorage} can work with arbitrary kinds of data defined
to live on a cell as long as the corresponding data type implements a
certain interface. As an example,
the abstract \texttt{TransferableQuadraturePointData} class provides
a generic interface to facilitate several low-level operations
that were previously tedious or technically challenging to implement.
\marginpar{Denis: It is not clear to me how \texttt{CellDataStorage} and
  \texttt{p::d::ContinuousQuadratureDataTransfer} relate to each
  other. Can you clarify the paragraph?}
For instance, the
\texttt{parallel::distributed::ContinuousQuadratureDataTransfer} class
assists in the transfer of arbitrary data (that is continuous within a
cell) stored at quadrature points when performing $h$-adaptive refinement of
\texttt{parallel::distributed::Triangulation}. Not only does it perform an
$L^2$-projection of the specified user data between quadrature
points, but it also ships the data automatically between MPI processes.

>>>>

The \texttt{CellDataStorage} templated class is an integrated mechanism to
store a vector of user-defined data within each cell,
such as a coefficient at each quadrature point.
Although the same was previously achieved through the use
of a cell's \texttt{user\_pointer}, it required users to manage this data
themselves, including transfer of this data if ownership of a cell is
transferred from one processor to another in parallel
computations. Instead, this data is now treated as a first-class
citizen in \dealii{}.

\texttt{CellDataStorage} can work with arbitrary kinds of data defined
to live on a cell as long as the corresponding data type implements a
certain interface. As an example,
the abstract \texttt{TransferableQuadraturePointData} class provides
a generic interface to facilitate several low-level operations
that were previously tedious or technically challenging to implement.
For instance, when user's custom data type is derived from \texttt{TransferableQuadraturePointData}
and stored at quadrature points using \texttt{CellDataStorage},
the \texttt{parallel::distributed::ContinuousQuadratureDataTransfer} class
can transfer this data (assuming that it is continuous within a cell)
when performing $h$-adaptive refinement of
\texttt{parallel::distributed::Triangulation}. Not only does it perform an
$L^2$-projection of the specified user data between quadrature
points, but it also ships the data automatically between MPI processes.
